---
title: "CTR-study_Rankings-io"
author: "Francois Delavy"
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float: true
editor_options: 
  chunk_output_type: console
---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
background-color: #00d188;
border-color: #00d188;
}

body {
font-family: 'Alegreya Sans', sans-serif;
color: #333333;
font-size: 14px;
}

h1 {
font-weight: bold;
font-size: 28px;
}

h1.title {
font-size: 30px;
color: #00d188;
}

h2 {
font-size: 24px;
}

h3 {
font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.showtext = TRUE, dpi = 700)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})

Sys.setlocale("LC_TIME", "C")
# extrafont::loadfonts(device = "win")
```



```{r prep}
## packages: remove or add your necessary packages

# required_packages <- c("tidyverse", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext")

required_packages <- c("tidyverse", "here", "colorspace", "pdftools", "kableExtra", "ggrepel")

for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
    require(i, character.only = T)
  }
}



## save plots?
save <- FALSE
#save <- FALSE

## quality of png's
dpi <- 750


## theme updates; please adjust to client´s website

base_size = 10

my_theme <- function(){
  theme_minimal() +
    theme(
      plot.margin = margin(30, 30, 30, 30),
      plot.background = element_rect(color = "white",
                                     fill = "white"),
      plot.title = element_text(size = 1.4 * base_size),
      plot.title.position = "plot",
      plot.subtitle = element_text(size = base_size),
      plot.caption = element_text(color = "grey40",
                                  size = 0.9 * base_size),
      plot.caption.position = "plot",
      axis.line.x = element_line(color = "black",
                                 size = .8),
      axis.line.y = element_line(color = "black",
                                 size = .8),
      axis.title.x = element_text(size =  base_size,
                                  face = "bold"),
      axis.title.y = element_text(size = base_size,
                                  face = "bold"),
      axis.text = element_text(size = 0.9 * base_size,
                               color = "black",
                               face = "bold"),
      # axis.ticks = element_blank(),
      axis.ticks = element_line(color = "black"),
      panel.grid.major.x = element_line(size = .4,
                                        color = "#eaeaea",
                                        linetype = "solid"),
      panel.grid.major.y = element_line(size = .4,
                                        color = "#eaeaea",
                                        linetype = "solid"),
      panel.grid.minor.x = element_line(size = .4,
                                        color = "#eaeaea",
                                        linetype = "solid"),
      panel.grid.minor.y = element_blank(),
      panel.spacing.x = unit(2, "lines"),
      panel.spacing.y = unit(1, "lines")
    )
}


## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)

## main colors rankings.io
r_col <- "#D21D5C"


```





# Load data


```{r data_loading}

results <- rio::import(here::here("proc_data", "proc_data.rds")) 



```


# Data exploration


```{r}

glimpse(results)

```

```{r, fig.align='center', fig.height=5, out.width='80%'}

results %>%
  ggplot() +
  geom_line(aes(x=date, y=rank, group=Sample_ID)) +
  # geom_smooth(aes(x=date, y=rank)) +
  geom_line(data = results %>% group_by(date) %>% summarize(avg = mean(rank, na.rm = TRUE)),
            aes(x=date, y=avg),
            color = r_col,
            size = 2) +
  my_theme() +
  scale_y_reverse(breaks = c(1,5,10,15,20,25,30)) +
  scale_x_date(
    breaks = c(min(results$date), "2021-03-12", "2021-03-12", "2021-03-19",
               "2021-03-26", "2021-04-02", max(results$date)),
    date_labels = "%d %b"
    # date_breaks = "1 week",
    # date_minor_breaks = "1 day"
  ) +
  labs(
    title = "Ranking Over Time" ,
    subtitle = "Ranking of all samples over time and their average in pink."
  )

if(save == T){ 
  ggsave(here::here("plots", "all_over_time.pdf"), name_plot, 
         width = 12.5, height = 8, device = cairo_pdf)
}

```

* Chaotic start, bump in the middle after 2 weeks, stabilization
* No large, clear, and major effect
* Need to average position for a few days to get stable estimate because variability ad missing values at the start.  

# Key Figures

## Average Ranking Improvement

```{r}

# average rank of first five days:
avg_start_1w <- results %>% filter(date < "2021-03-12") %>% 
  # first the first week average by sample:
  group_by(Sample_ID) %>% 
  summarize(avg = mean(rank, na.rm = TRUE)) %>% 
  # then the average of the samples:
  ungroup() %>%
  summarize(avg = mean(avg)) %>%
  as.numeric()

# average rank of last five days:
avg_end_1w <- results %>% filter(date > "2021-03-29") %>% 
  # first the first week average by sample:
  group_by(Sample_ID) %>% 
  summarize(avg = mean(rank, na.rm = TRUE)) %>% 
  # then the average of the samples:
  ungroup() %>%
  summarize(avg = mean(avg)) %>%
  as.numeric()

rank_gain = avg_start_1w - avg_end_1w


```

On average, the law firms gained `r round(rank_gain, 1)` ranks over the month (average of first week - average of last week).  

```{r, fig.align='center', fig.height=6, out.width='80%'}

all_avg_start_1w <- results %>% 
  filter(date < "2021-03-12") %>%
  group_by(Sample_ID) %>% 
  summarise(`First Week` = mean(rank, na.rm = TRUE))
all_avg_end_1w <- results %>% 
  filter(date > "2021-03-29") %>%
  group_by(Sample_ID) %>% 
  summarise(`Last Week` = mean(rank, na.rm = TRUE))

all_avg_wide = all_avg_start_1w %>% 
  left_join(all_avg_end_1w, by = "Sample_ID") %>%
  mutate(
    start_page = case_when(
      `First Week` <= 10 ~ 1,
      `First Week` > 10 &`First Week` <= 20 ~ 2,
      `First Week` > 20 ~ 3
    )
  )
all_avg_long <- all_avg_wide %>%
  pivot_longer(cols = c(2:3), names_to = "Week", values_to = "Average Rank")



# a slopegraph
ggplot(data = all_avg_long) +
  geom_line(aes(x = Week, y = `Average Rank`, group = Sample_ID)) +
  my_theme() +
  scale_y_reverse(breaks = c(1,5,10,15,20,25,30)) +
  labs(
    title = "Average Rank in First and Last Week",
    subtitle = "Pink: overall average\nGreen: average of those who started on first page\nOrange: average of those who started on second page\nRed: average of those who started on third (and fourth) page"
  ) +
  # average:
  geom_line(
    data = all_avg_long %>% group_by(Week) %>% summarise(avg = mean(`Average Rank`)),
    aes(x = Week, y = avg, group = 1),
    color = r_col,
    size = 1
  ) + geom_label_repel(
    data = all_avg_long %>% group_by(Week) %>% summarise(avg = mean(`Average Rank`)),
    aes(x = Week, y = avg, label = as.character(round(avg,1))), 
    size = 3, color = r_col
  ) + 
  # average of those started on first page:
  geom_line(
    data = all_avg_long %>% filter(start_page == 1) %>% group_by(Week) %>% 
      summarise(avg = mean(`Average Rank`)),
    aes(x = Week, y = avg, group = 1),
    color = "green",
    size = 1
  ) + geom_label_repel(
    data = all_avg_long %>% filter(start_page == 1) %>% group_by(Week) %>% 
      summarise(avg = mean(`Average Rank`)),
    aes(x = Week, y = avg, label = as.character(round(avg,1))), 
    size = 3, color = "green"
  ) + 
  # average of those started on 2nd page:
  geom_line(
    data = all_avg_long %>% filter(start_page == 2) %>% group_by(Week) %>% 
      summarise(avg = mean(`Average Rank`)),
    aes(x = Week, y = avg, group = 1),
    color = "orange",
    size = 1
  ) + geom_label_repel(
    data = all_avg_long %>% filter(start_page == 2) %>% group_by(Week) %>% 
      summarise(avg = mean(`Average Rank`)),
    aes(x = Week, y = avg, label = as.character(round(avg,1))), 
    size = 3, color = "orange"
  ) + 
  # average of those started on 3rd (and 4th) page:
  geom_line(
    data = all_avg_long %>% filter(start_page == 3) %>% group_by(Week) %>% 
      summarise(avg = mean(`Average Rank`)),
    aes(x = Week, y = avg, group = 1),
    color = "red",
    size = 1
  ) + geom_label_repel(
    data = all_avg_long %>% filter(start_page == 3) %>% group_by(Week) %>% 
      summarise(avg = mean(`Average Rank`)),
    aes(x = Week, y = avg, label = as.character(round(avg,1))), 
    size = 3, color = "red"
  )


```

* Different fate for the law firms. In particular two are plunging.
* No apparent difference in behavior in function of their start rank. Apparently a bit easier to improve if starting from lower rank. 


A *paired t-test* comparing the average ranking of each law firm during the first week and last week *shows that the difference is statistically significant*. We reject the null hypothesis that the difference in mean between the first week and last week in zero in favor of the alternative hypothesis: true difference in means is not equal to 0.  

```{r, echo = TRUE}

t.test(all_avg_wide$`First Week`,
       all_avg_wide$`Last Week`,
       paired=TRUE)

```


# Conclusions
* Improvement on average of 2 ranks in 1 month. Statistically significant improvement. 
* Rather small improvement in ranking.





